Another paper with lots of text and fancy pictures

### 2023-11-29 paper.tex
Fix images
Reorder images
Remove textcolor

Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
\cref{fig:heatmaps}. Anisotropicity of the both samples can be seen as a slower
decay of $S_3$ in one of the directions. Additionally, it can be observed that
elongated clusters of the void phase in the sample of soil are parallel to each
other and have a regular spacing about \textcolor{red}{$150 \mu m$}.

\begin{table}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
    Soil & XCT & $160 \times 160 \times 160$ & \textcolor{red}{2.25} & 0.9210 \\
    Shale & XCT & $160 \times 160 \times 160$ & \textcolor{red}{2.25} & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table}

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale-c3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropicity more visible. It can be observed that the samples have
    cavities elongated along the vector $(1, 1, 0)$.}
  \label{fig:heatmaps}
\end{figure*}

@@

Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
rotations or trial triangles. It is sensitive to anisotropicity of the medium
when it is stretched along one of the axes as shown in \cref{fig:aniso}. The
main advantage of our algorithm is its parallelizability and ease of
implementation. An equivalent operation for rotation of test triangles is a
rotation of the whole input image which we have implemented in our
CorrelationFunctions.jl package. By applying a rotation to the input first we
made a rest of the algorithm cache-friendly by avoiding random memory access.
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\linewidth]{images/aniso.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/aniso-s3-avg.png}
  \caption[]{$S_3$ function for anisotropic media (on the left) elongated along
    the vector $(1, 1)$. Anisotropicity of the medium can be seen on a heatmap
    of $S_3$ function (in the middle). An average of 120 $S_3$ evaluations of
    the medium rotated by a random angle is on the right.}
  \label{fig:aniso}
\end{figure}

>>>>

Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
\cref{fig:heatmaps}. Anisotropicity of the both samples can be seen as a slower
decay of $S_3$ in one of the directions. Additionally, it can be observed that
elongated clusters of the void phase in the sample of soil are parallel to each
other and have a regular spacing about $50 \mu m$.

\begin{table}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
    Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table}

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale-s3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropicity more visible. It can be observed that the samples have
    cavities elongated along the vector $(1, 1, 0)$.}
  \label{fig:heatmaps}
\end{figure*}

@@

Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
rotations or trial triangles. It is sensitive to anisotropicity of the medium
when it is stretched along one of the axes as shown in \cref{fig:aniso}. The
main advantage of our algorithm is its parallelizability and ease of
implementation. An equivalent operation for rotation of test triangles is a
rotation of the whole input image which we have implemented in our
CorrelationFunctions.jl package. By applying a rotation to the input first we
made a rest of the algorithm cache-friendly by avoiding random memory access.
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.4\linewidth, frame]{images/aniso.png}
  \vskip\baselineskip
  \includegraphics[width=0.45\linewidth]{images/aniso-s3.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/aniso-s3-avg.png}
  \caption[]{$S_3$ function for anisotropic media (on the left) elongated along
    the vector $(1, 1)$. Anisotropicity of the medium can be seen on a heatmap
    of $S_3$ function (in the middle). An average of 120 $S_3$ evaluations of
    the medium rotated by a random angle is on the right.}
  \label{fig:aniso}
\end{figure}
